\documentclass[a4paper]{article}

\usepackage{color}
\usepackage[british]{babel}
\usepackage[utf8]{inputenc}

\begin{document}

Ref. No.:  COMPAG-D-13-00254R1

Title: SURCOS: a software tool to simulate irrigation and fertigation in isolated furrows and furrow networks

Computers and Electronics in Agriculture

Qin Zhang, Ph.D.

Editor-in-Chief

Computers and Electronics in Agriculture

\textcolor{red}{Dear editor and reviewers, thank you for your valuable comments
and suggestions.}

\vspace{5mm}

Reviewers' comments:

\vspace{5mm}

Reviewer \#1:

The paper and case studies have been improved with further explanations and results presented in tables. Some modifications that would further improve the paper are:

The main window screengrab (Figure 3) and the plot selection window (Figure 9) are not descriptive and could be removed.

\textcolor{red}{ANSWER: Both figures have been removed following the reviewer's recommendation.}

The probes configuration windows (Figure 7) and advanced parameters configuration windows (Figure 8) are mostly blank space, could the input boxes be made bigger? 

\textcolor{red}{ANSWER: Both figures, as well as the inlet configuration panel, (figures 5-7 in the present manuscript) have been trimmed to avoid blank spaces.} 

The input parameters for each panel would be better presented as a table with parameters for each panel and the corresponding description, and/or a block diagram of the software. 
Section 4.2.4 is not descriptive and does not say which parameters are set. The parameters entered should be listed.


\textcolor{red}{ANSWER: Tables 2 and 3 have been added to describe the parameters of the furrow and fertilizer configuration panels. The parameters set on the
fertilizer configuration panel are now described in Section 4.2.4. The advanced configuration parameters are detailed in Section 4.2.6. In the other configuration panels (figures 3, 5, and 6) the authors consider that the corresponding figures are sufficiently clear to describe the parameters.}

\vspace{5mm}

Reviewer \#3: 

Dear Editor,

CC: Authors

I've reviewed the revised version of the manuscript COMPAG-D-13-0254R1 entitled "SURCOS: a software tool to simulate irrigation and fertigation in isolated furrows and furrow networks"
The authors successfully tracked all my recommendations to improve the quality of their manuscript; however, I noticed some additional notices which they have to consider.

1-	Highlights:
a.	H3: rewrite please, it is not clear.
b.	H4: better to say "previously verified and validated numerical method"
c.	H5: better to say "The program is fast, easy, and free", the word "freely downloaded" nowadays means that you can download it for free but you to pay when you use it!!

\textcolor{red}{ANSWER: The highlights are rewritten following the recommendations of the reviewer.}

2-	L40-42: I think this sentence should be reformulated or removed, as it is not clear whether the authors are criticizing or praising the mentioned works.

\textcolor{red}{ANSWER: The sentence has been rewritten, lines 40-41 ot the present manuscript.}

3-	L249-253: The descriptions of the C++ libraries should be put inline in the same paragraph.

\textcolor{red}{ANSWER: The descriptions are put inline in the current manuscript (lines 248-252).}

4-	The repetition of the name of the developed model (surcos) is not satisfactory, it is better to mention the name once in the paper in a sentence like {the currently developed model is named "surcos", the first part of the name stands for surface irrigation, and the second part stands for ….}. After that make the dominant mentions to be "the current model" or "the model", and sometimes use "surcos". Avoid usage of "Program surcos" as in L104, 125, 208, etc. as it is not perfect English. Either use "the model" or "surcos". 

\textcolor{red}{ANSWER: "Program surcos" has been replaced by "SURCOS" or "the model" following the reviewer's suggestion (changes in lines 103, 124, 207, 210, 246, 264, 300, 332, 437, 464 and captions of figures 2, 13, 14, 15 and table 1 of the present manuscript).}

5-	Fig 3 title: apply the above note to it as the model name already appears in the figure, the title should read "The main window of the current model"

\textcolor{red}{ANSWER: Figure 3 has been removed following the suggestion of reviewer \#1.}

6-	L263-264: the line should read "A window contains different panel to configure the simulations. The window can be accessed by pressing on the Configure button."

\textcolor{red}{ANSWER: Lines 261-262 in the present manuscript have been rewritten following the reviewer's recommendation.}

7-	Figure 6, 7, 8: Again, sorry, I am not asking the authors to change the build of the real model by the GTK+ library, but to crop the captured photos to the important parts in the interface, this saves space to the journal and looks better, I uploaded the 3 figures trimmed using SnagIt software as suggested on the editorial system. Please consider them or similar ones.

\textcolor{red}{ANSWER: The author are grateful to the reviewer for the figures. Sorry, we misunderstood the previous reviewer's comment. Figures 5, 6 and 7 in the current manuscript have been trimmed.}

8-	L293: can be set "here", not "too".

\textcolor{red}{ANSWER: "too" has been replaced by "here" (line 291).}

9-	Please revise all sections 4.1 to 4.2.6 especially the first lines under the title, revise them for English and for independency to other sections.

\textcolor{red}{ANSWER: The text in sections 4.1 to 4.2.6 has been revised.}

10-	I did not revise the references, so please be sure that all the references are mentioned in the text and vice versa, and they should meet the Journal's requirements.

\textcolor{red}{ANSWER: The manuscript has been written with LaTeX + BibTeX. These tools ensure that all the references mentioned in the text are present in the
references list (and vice versa) and meet the Journal's requirements (unless errors in the references database or in the Journal's LaTeX template). Nevertheless, the references list has been revised.}

Attachments: Figures 6, 7, 8 (in the editorial website)

Best regards


\end{document}
